%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Bram }{De Jaegher}
       {Bioscience engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Abelendreef 21
    8300 Knokke-Heist
    Belgium
    ~
    \href{mailto:bram.de.jaegher@gmail.com}{adrien@friggeri.net}
    \href{Moet nog weg}{http://friggeri.net}
    \href{Moet nog weg}{fb://adrien}
  \section{languages}
    Dutch \textit{native language}
    English \textit{C2: mastery}
    French  \textit{B2: upper-intermediate}
  \section{technical skills}
  Control theory (Class./Modern.)
  Machine learning
  CFD
  \section{programming}
  Working knowledge
  MATLAB/Simulink
  Python 2.7/3
  R
  LaTeX
  ~
  Basic knowledge
  CSS/HTML5
\end{aside}

\section{interests}


\section{education}

\begin{entrylist}
    \entry
    {2014–2016}
    {M.Sc. (In progress)}
    {Ghent university}
    {Bioscience engineering\\
    Chemistry and foodtechnology}
  \entry
    {2011-2014}
    {B.Sc. cum laude}
    {Ghent university}
    {Bioscience engineering\\
    Chemistry and Bioproces technology}
  \entry
    {2003}
    {French Baccalauréat S. with honors}
    {Lycée Louis le Grand, Paris}
    {Specialization in mathematics and physics}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {02–07 2009}
    {LIP6/CNRS, Paris}
    {Research Internship.}
    {\emph{Visualization of complex networks.}}
  \entry
    {06–08 2008}
    {ISCPIF/CNRS, Paris}
    {Research Internship.}
    {\emph{Diffusion in the Blogosphere. Happy Flu.}}
  \entry
    {06–08 2007}
    {LIP6/CNRS, Paris}
    {Research Internship.}
    {\emph{Kernels in real world networks.}}
  \entry
    {07–08 2005}
    {\href{http://www.kelkoo.com}{Kelkoo.com}}
    {Summer job.}
    {\emph{Creation of a keyword generator for Google Adwords.}}
  \entry
    {07–08 2004}
    {\href{http://www.monsieurprix.com}{MonsieurPrix.com}}
    {Summer job.}
    {\emph{Development of an e-commerce product indexation spider.}}
\end{entrylist}

\section{applications}

\begin{entrylist}
  \entry
    {2012}
    {Who did I forget ?}
    {\href{http://whodidiforget.com}{whodidiforget.com}}
    {Guest list recommendation for Facebook events based on friends already attending the event.}
  \entry
    {2011}
    {Fellows}
    {\href{http://fellows-exp.com}{fellows-exp.com}}
    {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
  \entry
    {2008}
    {Happy Flu}
    {\href{http://happyflu.com}{happyflu.com}}
    {Experiment aimed to measure viral spreading of content across the blogosphere.}
\end{entrylist}

\section{publications}

Put your publications here!

%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
